Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-29 tests-aniso-conduct.tex
Removed introductory paragraph.

In a plasma, conduction takes place primarily due to electron motion.
In astrophysical environments such as the intergalactic and
intracluster media, with typical magnetic strengths of $\sim 1$~$\mu$G
and temperatures in the millions of Kelvin, the electron gyroradius is
very small compared to the scales of interest in a typical
cosmological simulation.  As a result, electrons can only move
\textit{along} magnetic field lines, not perpendicular to them, which
can result in very interesting magnetohydrodynamical instabilities \protect \citep[e.g.,][]{2008ApJ...677L...9P,2008ApJ...688..905P}. The correct
modeling of this behavior can be quite challenging, and is described
in Section~\protect\ref{sec.num.conductions}. Conduction in \protect\enzo\ is calculated in both an operator-split and directionally-split manner,
and the addition of heat transport solely along magnetic field lines
requires computation of cross-terms in the temperature derivative at
cell faces, which can add spurious oscillations in the temperature
field in regions where the temperature gradient is strong in more than
one spatial direction unless an appropriate flux-limiter \protect\citep[such as that of][]{1977JCoPh..23..263V} is chosen.
\mqk{The previous paragraph more or less repeats what's in Section~\ref{sec.num.conductions}, I think it should be removed (or merged with that section).}

Figure~\ref{fig.conduct} shows a test that demonstrates the correct
behavior of anisotropic thermal conduction in \enzo.  We initialize a
two-dimensional, $256 \times 256$ cell simulation having a physical
scale of 1 kpc on a side, a uniform density of 1 proton cm$^{-3}$ and a
background temperature of $10^6$ Kelvin.  Magnetic fields with a
strength of B$_0 = 1$~$\mu$G are initialized such that the field lines
form circles around the center of the simulation volume, such that
B$_x = -B_0\sin(\theta)$ and B$_y = B_0\cos(\theta)$, where $\theta$
is the angle measured from the $+x$ direction in a counterclockwise
manner.  A Gaussian temperature pulse is injected at $(0.75, 0.5)$ (in
units of the box size), with a peak temperature of $10^8$ K and a FWHM
of $1/64$ of the box size.  This initial setup is shown in the left
panel of Figure~\ref{fig.conduct}.  The simulation is then allowed to
evolve with \textit{only} anisotropic conduction turned on (e.g., no
hydrodynamics, radiative cooling, or cosmological expansion), and with
a Spitzer fraction of f$_{\rm sp} = 1$.

>>>>

Figure~\ref{fig.conduct} shows a test that demonstrates the correct
behavior of anisotropic thermal conduction (see
Section~\ref{sec.num.conductions}) in \enzo. We initialize a
two-dimensional, $256 \times 256$ cell simulation having a physical
scale of 1 kpc on a side, a uniform density of 1 proton cm$^{-3}$ and
a background temperature of $10^6$ Kelvin.  Magnetic fields with a
strength of B$_0 = 1$~$\mu$G are initialized such that the field lines
form circles around the center of the simulation volume, such that
B$_x = -B_0\sin(\theta)$ and B$_y = B_0\cos(\theta)$, where $\theta$
is the angle measured from the $+x$ direction in a counterclockwise
manner.  A Gaussian temperature pulse is injected at $(0.75, 0.5)$ (in
units of the box size), with a peak temperature of $10^8$ K and a FWHM
of $1/64$ of the box size.  This initial setup is shown in the left
panel of Figure~\ref{fig.conduct}.  The simulation is then allowed to
evolve with \textit{only} anisotropic conduction turned on (e.g., no
hydrodynamics, radiative cooling, or cosmological expansion), and with
a Spitzer fraction of f$_{\rm sp} = 1$.
